---
title: "Introduction to genderstat"
author: "S M Mashrur Arafin Ayon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to genderstat}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Introduction

The `genderstat` package provides tools for quantitative analysis in gender studies. This includes computation of various gender inequality metrics and visualization tools.


## Gender Development Index (GDI)

The Gender Development Index (GDI) measures gender inequalities across three basic dimensions: health, knowledge, and living standards. 

```{r}
# Load the required data
library(genderstat)
data(real_data_GDI)

# Compute the GDI
gdi_results <- gender_development_index(real_data_GDI)
print(gdi_results)
```



## Visualizing Gender Development Index (GDI) and Human Development Index (HDI)

To gain insights into the gender inequalities across nations, we can visualize the Gender Development Index (GDI) and Human Development Index (HDI) for the bottom 15 countries.

```{r fig.width=10, fig.height=6}
# Load necessary libraries
library(genderstat)
library(ggplot2)
library(dplyr)
library(reshape2)

# Load the example dataset
data(real_data_GDI)

# Plot Gender Development Index (GDI) for Bottom 15 Countries
gdi_plot <- plot_gdi(real_data_GDI)
print(gdi_plot)

# Plot Human Development Index (HDI) for Bottom 15 Countries by Gender
hdi_plot <- plot_hdi(real_data_GDI)
print(hdi_plot)
```

## Visualizing Gender Inequality Index (GII)

### Bottom 15 Countries by Gender Inequality Index (GII)

The Gender Inequality Index (GII) is a composite measure reflecting inequality in achievements between women and men in three dimensions: reproductive health, empowerment, and the labor market. Here, we visualize the countries that are the worst performers according to the GII, highlighting the areas where gender inequality is most pronounced.

```{r, fig.width=10, fig.height=6}
# Load the required dataset
data(real_data_GII)

# Plot Gender Inequality Index (GII) for Bottom 15 Countries
gii_plot <- plot_gii(real_data_GII)
print(gii_plot)
```


