---
title: "Introduction to genderstat"
author: "S M Mashrur Arafin Ayon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to genderstat}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Introduction

The `genderstat` package provides tools for quantitative analysis in gender studies. This includes computation of various gender inequality metrics and visualization tools.


## Gender Empowerment Measure (GEM)

The Gender Empowerment Measure (GEM) evaluates gender equality in terms of economy, political participation, and decision making. 

```{r}
# Load the required libraries and data
data(real_data_GEM)

# Compute the GEM
gem_results <- gender_empowerment_measure(real_data_GEM)
print(gem_results)
```


## Gender Development Index (GDI)

The Gender Development Index (GDI) measures gender inequalities across three basic dimensions: health, knowledge, and living standards. 

```{r}
# Load the required data
data(real_data_GDI)

# Compute the GDI
gdi_results <- gender_development_index(real_data_GDI)
print(gdi_results)
```


